Constraint result to the self-interacting dark matter particle mass from the observational data

### 2025-06-11 article/article.tex
add dark matter annihilation

   \begin{table}
      \centering
      \begin{tabular}{ccl}
         \hline\hline
         $z$ & $H(z)$ & Reference \\
         \hline     
         0.07 & $69 \pm 19.6$ & \cite{Zhang_2014} \\
         0.09 & $69 \pm 12$ & \cite{PhysRevD.71.123001} \\
         0.12 & $68.6 \pm 26.2$ & \cite{Zhang_2014} \\
         0.17 & $83 \pm 8$ & \cite{PhysRevD.71.123001} \\
         0.179 & $75 \pm 4$ & \cite{M.Moresco_2012} \\
         0.199 & $75 \pm 5$ & \cite{M.Moresco_2012} \\
         0.2 & $72.9 \pm 29.6$ & \cite{Zhang_2014} \\
         0.27 & $77 \pm 14$ & \cite{PhysRevD.71.123001} \\
         0.28 & $88.8 \pm 36.6$ & \cite{Zhang_2014} \\
         0.352 & $83 \pm 14$ & \cite{M.Moresco_2012} \\
         0.3802 & $83 \pm 13.5$ & \cite{Moresco_2016}  \\
         0.4 & $95 \pm 17$ & \cite{PhysRevD.71.123001} \\
         0.4004 & $77 \pm 10.2$ & \cite{Moresco_2016} \\
         0.4247 & $87.1 \pm 11.2$ & \cite{Moresco_2016} \\
         0.4497 & $92.8 \pm 12.9$ & \cite{Moresco_2016} \\
         0.47 & $89 \pm 34$ & \cite{10.1093/mnras/stx301} \\
         0.4783 & $80.9 \pm 9$ & \cite{Moresco_2016} \\
         0.48 & $97 \pm 62$ & \cite{Daniel.Stern_2010} \\
         0.593 & $104 \pm 13$ & \cite{M.Moresco_2012} \\
         0.68 & $92 \pm 8$ & \cite{M.Moresco_2012} \\
         0.75 & $98.8 \pm 33.6$ & \cite{Borghi_2022} \\
         0.781 & $105 \pm 12$ & \cite{M.Moresco_2012} \\
         0.8 & $113.1 \pm 15.1$ & \cite{Jiao_2023} \\
         0.875 & $125 \pm 17$ & \cite{M.Moresco_2012} \\
         0.88 & $90 \pm 40$ & \cite{Daniel.Stern_2010} \\
         0.9 & $117 \pm 23$ & \cite{PhysRevD.71.123001} \\
         1.037 & $154 \pm 20$ & \cite{M.Moresco_2012} \\
         1.3 & $168 \pm 17$ & \cite{PhysRevD.71.123001} \\
         1.363 & $160 \pm 33.6$ & \cite{10.1093/mnrasl/slv037} \\
         1.43 & $177 \pm 18$ & \cite{PhysRevD.71.123001} \\
         1.53 & $140 \pm 14$ & \cite{PhysRevD.71.123001} \\
         1.75 & $202 \pm 40$ & \cite{PhysRevD.71.123001} \\
         1.965 & $186.5 \pm 50.4$ & \cite{10.1093/mnrasl/slv037} \\
         \hline\hline    
      \end{tabular}
      \caption{The OHD dataset from different reference.}
      \label{tab:1}
   \end{table}

@@

   \begin{table*}
      \centering
      \begin{tabular}{l|cccc}
         \hline\hline
         Dataset/Tracer & $z_{\text{eff}}$ & $D_{\text{V}}/r_{\text{d}}$ & 
         $D_{\text{M}}/r_{\text{d}}$ & $D_{\text{H}}/r_{\text{d}}$ \\
         \hline
         \textbf{SDSS-IV} \\
         MGS & 0.15 & $4.51 \pm 0.14$ & --- & --- \\
         BOSS galaxy & 0.38 & --- & $10.27 \pm 0.15$ & $24.89 \pm 0.58$ \\
         BOSS galaxy & 0.51 & --- & $13.38 \pm 0.18$ & $22.43 \pm 0.48$ \\
         eBOSS LRG & 0.70 & --- & $17.65 \pm 0.30$ & $19.78 \pm 0.46$ \\
         eBOSS ELG & 0.85 & --- & $19.5 \pm 1.0$ & $19.6 \pm 2.1$ \\
         eBOSS quasar& 1.48 & --- & $30.21 \pm 0.79$ & $13.23 \pm 0.47$ \\
         Ly$\alpha$-Ly$\alpha$ & 2.33 & --- & $37.6 \pm 1.9$ & $8.93 \pm 0.28$ \\
         Ly$\alpha$-quasar & 2.33 & --- & $37.3 \pm 1.7$ & $9.08 \pm 0.34$ \\
         \hline\hline
         \textbf{DESI DR2} \\ 
         BGS & 0.295 & $7.942 \pm 0.075$  & --- & --- \\
         LRG1 & 0.510 & $12.720 \pm 0.099$ & $13.588 \pm 0.167$ & $21.863 \pm 0.425$ \\
         LRG2 & 0.706 & $16.050 \pm 0.110$ & $17.351 \pm 0.177$ & $19.455 \pm 0.330$ \\
         LRG3+ELG1 & 0.934 & $19.721 \pm 0.091$ & $21.576 \pm 0.152$ & $17.641 \pm 0.193$ \\
         ELG2 & 1.321 & $24.252 \pm 0.174$ & $27.601 \pm 0.318$ & $14.176 \pm 0.221$ \\
         QSO & 1.484 & $26.055 \pm 0.398$ & $30.512 \pm 0.760$ & $12.817 \pm 0.516$ \\
         Ly$\alpha$ & 2.330 & $31.267 \pm 0.256$ & $38.988 \pm 0.531$ & $8.632 \pm 0.101$ \\
         \hline
         LRG3 & 0.922 & $19.656 \pm 0.105$ & $21.648 \pm 0.178$ & $17.577 \pm 0.213$ \\
         ELG1 & 0.955 & $20.008 \pm 0.183$ & $21.707 \pm 0.335$ & $17.803 \pm 0.297$ \\    
         \hline\hline
      \end{tabular}
      \caption{The BAO+RSD measurements dataset from SDSS-IV and DESI DR2.}
      \label{tab:2}
   \end{table*}

@@

   \begin{table}
      \centering
      \begin{tabular}{lll}
         \hline\hline
         parameter & initial & prior \\
         \hline
         $\Omega_{2,0}$ & 0.3 & $\mathcal{U}[0.0,1.0]$ \\
         $\log_{10}(\kappa C_1/$Gyr${}^{-1})$ & --- & $\mathcal{U}[-10,0]$ \\
         $n$ & 0 & $\mathcal{U}[-5,5]$ \\
         \hline
         $H_0$[km/(s$\cdot$Mpc)] & 70 & $\mathcal{U}[60,80]$ \\
         $r_{\text{d}}h$[Mpc] & 100 & $\mathcal{U}[50,150]$ \\
         \hline
      \end{tabular}
      \caption{Parameters and priors used in analysis. 
      All of the priors are flat in the ranges given. 
      The $\log_{10}(\kappa C_1)$ does not have a predicted value, 
      and the initial value of each chain is selected randomly uniformly
      within the prior range.}
      \label{tab:3}
   \end{table}

   The Eq.(\ref{eq:8}) convergant to the flat ΛCDM model as
   $\log_{10}(\kappa C_1)\to-\infty$, thus the constraints
   could only give the upper limit of what, and we use the
   95\% quantiles to determine the upper bounds of the parameters. 
   The constraint results are shown in 
   Figure \ref{fig:1}-\ref{fig:3} and summarized in Table \ref{tab:4}.

   For the dataset which cannot give a constraint to $H_0$, 
   we use $h \simeq 0.7$ as the default value to calculate the 
   annihilation parameter $\kappa$.

   \begin{table*}
      \centering
      \begin{tabular}{l|ccccc}
         \hline\hline
         Model/Dataset & $\Omega_{2,0}$ & $\log_{10}(\kappa C_1/$Gyr${}^{-1})$ & $10^{15}\kappa$[cm${}^3$/(s$\cdot$GeV)] & $n$ & $w_{\text{IDM}}$ \\
         \hline
         \textbf{Model 1} \\
         SNe Ia & $0.380 \pm 0.020$ & $<-3.05$ & $<8.82$ & --- & --- \\
         BAO & $0.2980 \pm 0.0070$ & $<-3.66$ & $<1.91$ & --- & --- \\
         BAO + SNe Ia + OHD & $0.3079_{-0.0067}^{+0.0051}$ & $<-3.99$ & $<0.907$ & --- & --- \\
         \hline
         \textbf{Model 2 ($\kappa=0$)} \\
         SNe Ia & $0.215_{-0.073}^{+0.10}$ & --- & --- & $-0.82_{-0.45}^{+0.29}$ & $-0.73_{-0.10}^{+0.15}$ \\
         BAO & $0.2952 \pm 0.0073$ & --- & --- & $-0.29_{-0.18}^{+0.15}$ & $-0.90_{-0.05}^{+0.06}$ \\
         BAO + SNe Ia + OHD & $0.2945 \pm 0.0075$ & --- & --- & $-0.42 \pm 0.11$ & $-0.86 \pm 0.04$ \\
         \hline
         \textbf{Model 2 ($\kappa\neq0$)} \\
         SNe Ia & $0.143_{-0.11}^{+0.067}$ & $<-2.15$ & $<50.7$ &  $-1.17_{-0.35}^{+0.17}$ & $-0.61_{-0.06}^{+0.12}$ \\
         BAO & $0.287_{-0.0022}^{+0.017}$ & $<-2.44$ & $<31.3$ & $-0.34_{-0.17}^{+0.22}$ & $-0.89_{-0.07}^{+0.06}$ \\
         BAO + SNe Ia + OHD & $0.241 \pm 0.062$ & $<-1.90$ & $<101.8$ & $-0.73_{-0.24}^{+0.33}$ & $-0.76_{-0.11}^{+0.08}$ \\
         \hline\hline
      \end{tabular}
      \caption{The constraint results of the IDM model.}
      \label{tab:4}
   \end{table*}

\subsection{Compared with other results}

   \begin{figure*}
      \centering
      \caption{The constraint result from the supernovae Ia data
      (left), the BAO data (middle) and the BAO + SNe Ia + OHD data (right).}
      \label{fig:1}
   \end{figure*}

   The SNe Ia dataset gives a value $\Omega_{2,0} \simeq 0.38$. The constraint result to Pantheon+
   SNe Ia dataset in the flat $\Lambda$CDM model is $\Omega_{m} \simeq 0.33$ (\cite{Borghi_2022}),

   \begin{figure*}
      \centering
      \caption{The constraint result from the supernovae Ia data
      (left), the BAO data (middle) and the BAO + SNe Ia + OHD data (right).}
      \label{fig:2}
   \end{figure*}

@@

   \begin{equation}
      Const=\mathcal{F}(-\infty)\equiv\lim_{x\to-\infty}\mathcal{F}(x)=
      \frac{\kappa C_1\ln\kappa C_1}{9H_0^4\Omega_{1,0}^2-4H_0^2\Omega_{1,0}(\kappa C_1)^2}.
   \end{equation}
   The initial time of today $t_0$ can be easily given as
   \begin{equation}
      t_0=2H_0^2\Omega_{1,0}[\mathcal{F}(-\infty)-\mathcal{F}(-H_0)],
   \end{equation}
   and the redshift $z_{\max}$ can be calculated as
   \begin{equation}
      z_{\max}=\exp\left[2H_0^2\Omega_{1,0}\int_{-\infty}^{-H_0}[\mathcal{F}(-\infty)
      -\mathcal{F}(x)]\mathrm{d}x+H_0t_0\right]-1,
   \end{equation}
   and $z_{\max}$ is also a function of $\Omega_{2,0}, \kappa C_1$ and $H_0$.
   \begin{figure}
      \centering
      \includegraphics[width=0.7\textwidth]{zmax.pdf}
      \caption{The redshift $z_{\max}$ as $H_0=70$ km/s/Mpc}
      \label{fig:3}
   \end{figure}

>>>>

   \begin{table}
      \centering
      \begin{tabular}{ccl}
         \hline\hline
         $z$ & $H(z)$ & Reference \\
         \hline     
         0.07 & $69 \pm 19.6$ & \cite{Zhang_2014} \\
         0.09 & $69 \pm 12$ & \cite{PhysRevD.71.123001} \\
         0.12 & $68.6 \pm 26.2$ & \cite{Zhang_2014} \\
         0.17 & $83 \pm 8$ & \cite{PhysRevD.71.123001} \\
         0.179 & $75 \pm 4$ & \cite{M.Moresco_2012} \\
         0.199 & $75 \pm 5$ & \cite{M.Moresco_2012} \\
         0.2 & $72.9 \pm 29.6$ & \cite{Zhang_2014} \\
         0.27 & $77 \pm 14$ & \cite{PhysRevD.71.123001} \\
         0.28 & $88.8 \pm 36.6$ & \cite{Zhang_2014} \\
         0.352 & $83 \pm 14$ & \cite{M.Moresco_2012} \\
         0.3802 & $83 \pm 13.5$ & \cite{Moresco_2016}  \\
         0.4 & $95 \pm 17$ & \cite{PhysRevD.71.123001} \\
         0.4004 & $77 \pm 10.2$ & \cite{Moresco_2016} \\
         0.4247 & $87.1 \pm 11.2$ & \cite{Moresco_2016} \\
         0.4497 & $92.8 \pm 12.9$ & \cite{Moresco_2016} \\
         0.47 & $89 \pm 34$ & \cite{10.1093/mnras/stx301} \\
         0.4783 & $80.9 \pm 9$ & \cite{Moresco_2016} \\
         0.48 & $97 \pm 62$ & \cite{Daniel.Stern_2010} \\
         0.593 & $104 \pm 13$ & \cite{M.Moresco_2012} \\
         0.68 & $92 \pm 8$ & \cite{M.Moresco_2012} \\
         0.75 & $98.8 \pm 33.6$ & \cite{Borghi_2022} \\
         0.781 & $105 \pm 12$ & \cite{M.Moresco_2012} \\
         0.8 & $113.1 \pm 15.1$ & \cite{Jiao_2023} \\
         0.875 & $125 \pm 17$ & \cite{M.Moresco_2012} \\
         0.88 & $90 \pm 40$ & \cite{Daniel.Stern_2010} \\
         0.9 & $117 \pm 23$ & \cite{PhysRevD.71.123001} \\
         1.037 & $154 \pm 20$ & \cite{M.Moresco_2012} \\
         1.3 & $168 \pm 17$ & \cite{PhysRevD.71.123001} \\
         1.363 & $160 \pm 33.6$ & \cite{10.1093/mnrasl/slv037} \\
         1.43 & $177 \pm 18$ & \cite{PhysRevD.71.123001} \\
         1.53 & $140 \pm 14$ & \cite{PhysRevD.71.123001} \\
         1.75 & $202 \pm 40$ & \cite{PhysRevD.71.123001} \\
         1.965 & $186.5 \pm 50.4$ & \cite{10.1093/mnrasl/slv037} \\
         \hline\hline    
      \end{tabular}
      \caption{
         The OHD dataset from different reference.
      }
      \label{tab:1}
   \end{table}

@@

   \begin{table*}
      \centering
      \begin{tabular}{l|cccc}
         \hline\hline
         Dataset/Tracer & $z_{\text{eff}}$ & $D_{\text{V}}/r_{\text{d}}$ & 
         $D_{\text{M}}/r_{\text{d}}$ & $D_{\text{H}}/r_{\text{d}}$ \\
         \hline
         \textbf{SDSS-IV} \\
         MGS & 0.15 & $4.51 \pm 0.14$ & --- & --- \\
         BOSS galaxy & 0.38 & --- & $10.27 \pm 0.15$ & $24.89 \pm 0.58$ \\
         BOSS galaxy & 0.51 & --- & $13.38 \pm 0.18$ & $22.43 \pm 0.48$ \\
         eBOSS LRG & 0.70 & --- & $17.65 \pm 0.30$ & $19.78 \pm 0.46$ \\
         eBOSS ELG & 0.85 & --- & $19.5 \pm 1.0$ & $19.6 \pm 2.1$ \\
         eBOSS quasar& 1.48 & --- & $30.21 \pm 0.79$ & $13.23 \pm 0.47$ \\
         Ly$\alpha$-Ly$\alpha$ & 2.33 & --- & $37.6 \pm 1.9$ & $8.93 \pm 0.28$ \\
         Ly$\alpha$-quasar & 2.33 & --- & $37.3 \pm 1.7$ & $9.08 \pm 0.34$ \\
         \hline\hline
         \textbf{DESI DR2} \\ 
         BGS & 0.295 & $7.942 \pm 0.075$  & --- & --- \\
         LRG1 & 0.510 & $12.720 \pm 0.099$ & $13.588 \pm 0.167$ & $21.863 \pm 0.425$ \\
         LRG2 & 0.706 & $16.050 \pm 0.110$ & $17.351 \pm 0.177$ & $19.455 \pm 0.330$ \\
         LRG3+ELG1 & 0.934 & $19.721 \pm 0.091$ & $21.576 \pm 0.152$ & $17.641 \pm 0.193$ \\
         ELG2 & 1.321 & $24.252 \pm 0.174$ & $27.601 \pm 0.318$ & $14.176 \pm 0.221$ \\
         QSO & 1.484 & $26.055 \pm 0.398$ & $30.512 \pm 0.760$ & $12.817 \pm 0.516$ \\
         Ly$\alpha$ & 2.330 & $31.267 \pm 0.256$ & $38.988 \pm 0.531$ & $8.632 \pm 0.101$ \\
         \hline
         LRG3 & 0.922 & $19.656 \pm 0.105$ & $21.648 \pm 0.178$ & $17.577 \pm 0.213$ \\
         ELG1 & 0.955 & $20.008 \pm 0.183$ & $21.707 \pm 0.335$ & $17.803 \pm 0.297$ \\    
         \hline\hline
      \end{tabular}
      \caption{
         The BAO+RSD measurements dataset from SDSS-IV and DESI DR2.
      }
      \label{tab:2}
   \end{table*}

@@

   \begin{table}
      \centering
      \begin{tabular}{lll}
         \hline\hline
         parameter & initial & prior \\
         \hline
         $\Omega_{2,0}$ & 0.3 & $\mathcal{U}[0.0,1.0]$ \\
         $\log_{10}(\kappa C_1/$Gyr${}^{-1})$ & --- & $\mathcal{U}[-10,0]$ \\
         $n$ & 0 & $\mathcal{U}[-5,5]$ \\
         \hline
         $H_0$[km/(s$\cdot$Mpc)] & 70 & $\mathcal{U}[60,80]$ \\
         $r_{\text{d}}h$[Mpc] & 100 & $\mathcal{U}[50,150]$ \\
         \hline
      \end{tabular}
      \caption{
         Parameters and priors used in analysis. 
         All of the priors are flat in the ranges given. 
         The $\log_{10}(\kappa C_1)$ does not have a predicted value, 
         and the initial value of each chain is selected randomly uniformly
         within the prior range.
      }
      \label{tab:3}
   \end{table}

   The Eq.(\ref{eq:8}) convergant to the flat ΛCDM model as
   $\log_{10}(\kappa C_1)\to-\infty$, thus the constraints
   could only give the upper limit of what, and we use the
   95\% quantiles to determine the upper bounds of the parameters. 
   The constraint results are shown in 
   Figure \ref{fig:1}-\ref{fig:2} and summarized in Table \ref{tab:4}.

   For the dataset which cannot give a constraint to $H_0$, 
   we use $h \simeq 0.7$ as the default value to calculate the 
   annihilation parameter $\kappa$.
   The constraint result to the upper limit of the annihilation parameter 
   is given in Table \ref{tab:4}, which reaches a value of $\kappa = 9.07 \times 10^{-16}$ cm${}^3$/(s$\cdot$GeV) in Model 1, 
   and $1.02 \times 10^{-13}$ cm${}^3$/(s$\cdot$GeV) in Model 2 with $\kappa\neq0$ at 95\% confidence level, respectively.

   \begin{figure*}
      \centering
      \subfigure{
         \includegraphics[width=0.45\textwidth]{model1.pdf}
      }
      \subfigure{
         \includegraphics[width=0.45\textwidth]{model2.pdf}
      }
      \caption{
         68\% and 95\% confidence level contours for parameters in 
         IDM model. The blue, orange and green contours are the results from
         the SNe Ia dataset, the BAO dataset and the BAO + SNe Ia + OHD dataset, respectively.
         \emph{Left panel}: constraint results to $\Omega_{2,0}$ and 
         $\log_{10}(\kappa C_1/$Gyr${}^{-1})$ in Model 1. 
         \emph{Right panel}: constraint results to $\Omega_{2,0}$ and $n$ in Model 2. 
         The dashed line is $n=0$, what implies $w_{\text{IDM}}=-1$.
      }
      \label{fig:1}
   \end{figure*}

   \begin{figure*}
      \centering
      \includegraphics[width=0.9\textwidth]{model2_kneq0.pdf}
      \caption{
         Marginalized 68\% and 95\% posterior constraints on $\Omega_{2,0}$, 
         $\log_{10}(\kappa C_1/$Gyr${}^{-1})$ and $n$ in Model 2 with $\kappa\neq0$,
         from the SNe Ia dataset (blue), the BAO dataset (orange) and the 
         combination of BAO + SNe Ia + OHD dataset (green). Noted that
         the combination of BAO + SNe Ia + OHD dataset gives a two-side constraint
         to the parameter $\log_{10}(\kappa C_1/$Gyr${}^{-1})$, while we still
         use the 95\% quantile upper limit to give the constraint.
         The dashed line is $n=0$, what implies $w_{\text{IDM}}=-1$.
      }
      \label{fig:2}
   \end{figure*}

   \begin{table*}
      \centering
      \begin{tabular}{l|ccccc}
         \hline\hline
         Model/Dataset & $\Omega_{2,0}$ & $\log_{10}(\kappa C_1/$Gyr${}^{-1})$ & $10^{15}\kappa$[cm${}^3$/(s$\cdot$GeV)] & $n$ & $w_{\text{IDM}}$ \\
         \hline
         \textbf{Model 1} \\
         SNe Ia & $0.380 \pm 0.020$ & $<-3.05$ & $<8.82$ & --- & --- \\
         BAO & $0.2980 \pm 0.0070$ & $<-3.66$ & $<1.91$ & --- & --- \\
         BAO+SNe Ia+OHD & $0.3079_{-0.0067}^{+0.0051}$ & $<-3.99$ & $<0.907$ & --- & --- \\
         \hline
         \textbf{Model 2 ($\kappa=0$)} \\
         SNe Ia & $0.215_{-0.073}^{+0.10}$ & --- & --- & $-0.82_{-0.45}^{+0.29}$ & $-0.73_{-0.10}^{+0.15}$ \\
         BAO & $0.2952 \pm 0.0073$ & --- & --- & $-0.29_{-0.18}^{+0.15}$ & $-0.90_{-0.05}^{+0.06}$ \\
         BAO+SNe Ia+OHD & $0.2945 \pm 0.0075$ & --- & --- & $-0.42 \pm 0.11$ & $-0.86 \pm 0.04$ \\
         \hline
         \textbf{Model 2 ($\kappa\neq0$)} \\
         SNe Ia & $0.143_{-0.11}^{+0.067}$ & $<-2.15$ & $<50.7$ &  $-1.17_{-0.35}^{+0.17}$ & $-0.61_{-0.06}^{+0.12}$ \\
         BAO & $0.287_{-0.0022}^{+0.017}$ & $<-2.44$ & $<31.3$ & $-0.34_{-0.17}^{+0.22}$ & $-0.89_{-0.07}^{+0.06}$ \\
         BAO+SNe Ia+OHD & $0.241 \pm 0.062$ & $<-1.90$ & $<101.8$ & $-0.73_{-0.24}^{+0.33}$ & $-0.76_{-0.11}^{+0.08}$ \\
         \hline\hline
      \end{tabular}
      \caption{
         Summary table of the parameter constraints from the different datasets in
         the IDM model. Results for the parameters $\Omega_{2,0}$ and $n$ are the
         mean values with 68\% confidence level, while the $\log_{10}(\kappa C_1)$
         is the 95\% quantile upper limit.
      }
      \label{tab:4}
   \end{table*}

\subsection{The dark matter annihilation}

   We assume that the dark matter particle $\chi$ consists of Weakly Interacting Massive Particles (WIMPs),
   which can annihilate into Standard Model (SM) particles with a cross section $\langle\sigma v\rangle$, 
   and the dark matter particle in the IDM model acts as a self-annihilation process.

   The WIMPs assumption gives that the thermal relic abundance of dark matter requires 
   an annihilation cross section of $\langle\sigma v \rangle $ about $ 3\times 10^{-26}$ cm${}^3$/s
   to match the observed cosmological density
   (\cite{PhysRevLett.39.165,annurev:/content/journals/10.1146/annurev.ns.29.120179.001525, GONDOLO1991145}).
   Adopting this value in the IDM model, the lower limit of the dark matter particle mass can be given as
   $M_{\chi} \gtrsim 3 \times 10^{-2}$ eV in Model 1 and 
   $3 \times 10^{-4}$ eV in Model 2 with $\kappa\neq0$.

   \begin{figure*}
      \centering
      \includegraphics[width=0.9\textwidth]{dm_ann.pdf}
      \caption{The dark matter annihilation cross section $\langle\sigma v\rangle$ 
         as a function of the dark matter particle mass $M_{\chi}$ in the IDM model.
      }
      \label{fig:3}
   \end{figure*}

@@

   \begin{equation}
      Const=\mathcal{F}(-\infty)\equiv\lim_{x\to-\infty}\mathcal{F}(x)=
      \frac{\kappa C_1\ln\kappa C_1}{9H_0^4\Omega_{1,0}^2-4H_0^2\Omega_{1,0}(\kappa C_1)^2}.
   \end{equation}
   The initial time of today $t_0$ can be easily given as
   \begin{equation}
      t_0=2H_0^2\Omega_{1,0}[\mathcal{F}(-\infty)-\mathcal{F}(-H_0)],
   \end{equation}
   and the redshift $z_{\max}$ can be calculated as
   \begin{equation}
      z_{\max}=\exp\left[2H_0^2\Omega_{1,0}\int_{-\infty}^{-H_0}[\mathcal{F}(-\infty)
      -\mathcal{F}(x)]\mathrm{d}x+H_0t_0\right]-1,
   \end{equation}
   and $z_{\max}$ is also a function of $\Omega_{2,0}, \kappa C_1$ and $H_0$.
   \begin{figure}
      \centering
      \includegraphics[width=0.7\textwidth]{zmax.pdf}
      \caption{The redshift $z_{\max}$ as $H_0=70$ km/(s$\cdot$Mpc)}
      \label{fig:3}
   \end{figure}
